Competing Bandits: The Perils of Exploration under Competition

### 2018-09-02 paper/competing_bandits.tex
Added \MRV macro.
Fixed the preamble as per the AAAI reqs, added section numbers.
restructure the paper a bit
attempt to make the figures look better

\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage{subfiles}
\usepackage{graphicx}
\usepackage{tikz} % SW: Added for plots
\frenchspacing

%\usepackage[utf8]{inputenc} % allow utf-8 input -- cannot use with AAAI! A.S.
%\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{natbib} % cannot use with AAAI! A.S.

\usepackage{amsthm} % The amsthm package provides extended theorem environments
\usepackage{float}
\usepackage{sgame, tikz} % Game theory packages
\usepackage{caption}
\usepackage{algorithm,algpseudocode}
\usepackage{makecell}
 \usepackage{multirow}
 \usepackage{graphicx}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{finding}{Finding}
\captionsetup{font=footnotesize}

@@

@@

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{url}
\usepackage{graphicx}
\frenchspacing
% Add additional packages here. The following
% packages may NOT be used  (this list
% is not exhaustive:
% authblk, caption, CJK, float, fullpage, geometry,
%hyperref, layout, nameref, natbib, savetrees,
%setspace, titlesec, tocbibind, ulem
%
%US Lettersize Paper Is Required
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
%
%
% PDFINFO
% You are required to complete the following
% for pass-through to the PDF.
% No LaTeX commands of any kind may be
% entered. The parentheses and spaces
% are an integral part of the
% pdfinfo script and must not be removed.
%
\pdfinfo{
/Title  (Competing Bandits: The Perils of Exploration under Competition)
/Author (Guy Aridor, Kevin Liu, Aleksandrs Slivkins, Zhiwei Steven Wu)
/Keywords (Input your keywords in this optional area)
}
%
%Section Numbers
% Uncomment if you want to use section numbers
% and change the 0 to a 1 or 2
 \setcounter{secnumdepth}{2} % section & subsection numbers

% Title and Author Information Must Immediately Follow
% the pdfinfo within the preamble
%

%\usepackage[utf8]{inputenc} % allow utf-8 input -- cannot use with AAAI! A.S.
%\usepackage{hyperref}       % hyperlinks
\usepackage{tikz} % SW: Added for plots
\usepackage{subfiles}
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage{amsmath,amssymb,amsfonts}
%\usepackage{natbib} % cannot use with AAAI! A.S.

\usepackage{amsthm} % The amsthm package provides extended theorem environments
\usepackage{float}
\usepackage{sgame, tikz} % Game theory packages
\usepackage{caption}
\usepackage{algorithm,algpseudocode}
\usepackage{makecell}
 \usepackage{multirow}
 \usepackage{graphicx}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newtheorem{finding}[definition]{Finding}
\newtheorem{conjecture}[definition]{Conjecture}
\captionsetup{font=footnotesize}

@@

\newcommand{\MRV}{mean reward vector\xspace} % mean reward vector
\newcommand{\MRVs}{mean reward vectors\xspace} % mean reward vector

@@

\subfile{content/revisited}

@@

### 2018-09-02 paper/content/barriers.tex
attempt to make the figures look better

\begin{table}[ht]
\centering
\caption{Reputation Erased Experiment, Heavy Tail}
\begin{tabular}{c@{\hspace{1.0\tabcolsep}}ccc}
  \hline
 & TS & DEG &  DG \\
  \hline
TS & \makecell{\textbf{ 0.016 } $\pm$ 0.0075 \\Var: 0.01 \\ ES: 100 \%} & \makecell{\textbf{ 0.13 } $\pm$ 0.02 \\Var: 0.1 \\ ES: 97 \%} & \makecell{\textbf{ 0.2 } $\pm$ 0.024 \\Var: 0.1 \\ ES: 96 \%} \\
  DEG & \makecell{\textbf{ 0.068 } $\pm$ 0.013 \\Var: 0.05 \\ ES: 93 \%} & \makecell{\textbf{ 0.29 } $\pm$ 0.024 \\Var: 0.2 \\ ES: 75 \%} & \makecell{\textbf{ 0.26 } $\pm$ 0.024 \\Var: 0.2 \\ ES: 80 \%} \\
   DG & \makecell{\textbf{ 0.15 } $\pm$ 0.019 \\Var: 0.1 \\ ES: 87 \%} & \makecell{\textbf{ 0.38 } $\pm$ 0.028 \\Var: 0.2 \\ ES: 80 \%} & \makecell{\textbf{ 0.33 } $\pm$ 0.024 \\Var: 0.2 \\ ES: 67 \%} \\
   \hline
   \label{rep_erase}
\end{tabular}
\end{table}
% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Sun Jul 22 14:23:06 2018
\begin{table}[ht]
\centering
\caption{Information Erased Experiment, Heavy Tail}
\begin{tabular}{c@{\hspace{1.0\tabcolsep}}ccc}
  \hline
 & TS & DEG &  DG \\
  \hline
TS & \makecell{\textbf{ 0.024 } $\pm$ 0.0094 \\Var: 0.02 \\ ES: 100 \%} & \makecell{\textbf{ 0.16 } $\pm$ 0.022 \\Var: 0.1 \\ ES: 97 \%} & \makecell{\textbf{ 0.22 } $\pm$ 0.025 \\Var: 0.2 \\ ES: 95 \%} \\
  DEG & \makecell{\textbf{ 0.24 } $\pm$ 0.025 \\Var: 0.2 \\ ES: 94 \%} & \makecell{\textbf{ 0.29 } $\pm$ 0.024 \\Var: 0.1 \\ ES: 72 \%} & \makecell{\textbf{ 0.27 } $\pm$ 0.024 \\Var: 0.1 \\ ES: 76 \%} \\
   DG & \makecell{\textbf{ 0.33 } $\pm$ 0.028 \\Var: 0.2 \\ ES: 94 \%} & \makecell{\textbf{ 0.38 } $\pm$ 0.026 \\Var: 0.2 \\ ES: 74 \%} & \makecell{\textbf{ 0.33 } $\pm$ 0.023 \\Var: 0.1 \\ ES: 58 \%} \\
   \hline
   \label{info_erase}
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
\centering
\caption{Information Erased Experiment Heavy Tail} 
\begin{tabular}{c@{\hspace{0.1\tabcolsep}}ccc}
\hline
\multicolumn{4}{c}{Incumbent Algorithm}\\
\multirow{12}{0.6in}{\rotatebox{90}{Entrant Algorithm}} \\
  \hline
 & TS & DEG &  DG \\ 
  \hline
TS & \makecell{\textbf{0.021} $\pm$0.009\\Var:0.02\\ES:100\%} & \makecell{\textbf{0.16} $\pm$0.02\\Var:0.1\\ES:97\%} & \makecell{\textbf{0.21} $\pm$0.02\\Var:0.2\\ES:95\%} \\ 
  DEG & \makecell{\textbf{0.26} $\pm$0.03\\Var:0.2\\ES:95\%} & \makecell{\textbf{0.3} $\pm$0.02\\Var:0.2\\ES:74\%} & \makecell{\textbf{0.26} $\pm$0.02\\Var:0.1\\ES:76\%} \\ 
   DG & \makecell{\textbf{0.34} $\pm$0.03\\Var:0.2\\ES:94\%} & \makecell{\textbf{0.4} $\pm$0.03\\Var:0.2\\ES:74\%} & \makecell{\textbf{0.33} $\pm$0.02\\Var:0.1\\ES:58\%} \\ 
   \hline
  \label{info_erase}
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Reputation Erased Experiment Heavy Tail} 
\begin{tabular}{c@{\hspace{0.01\tabcolsep}}ccc}
\hline
\multicolumn{4}{c}{Incumbent Algorithm}\\
\multirow{12}{0.6in}{\rotatebox{90}{Entrant Algorithm}} \\
  \hline
 & TS & DEG &  DG \\ 
  \hline
TS & \makecell{\textbf{0.0096} $\pm$0.006\\Var:0.009\\ES:100\%} & \makecell{\textbf{0.11} $\pm$0.02\\Var:0.09\\ES:98\%} & \makecell{\textbf{0.18} $\pm$0.02\\Var:0.1\\ES:95\%} \\ 
  DEG & \makecell{\textbf{0.073} $\pm$0.01\\Var:0.05\\ES:93\%} & \makecell{\textbf{0.29} $\pm$0.02\\Var:0.2\\ES:78\%} & \makecell{\textbf{0.25} $\pm$0.02\\Var:0.1\\ES:79\%} \\ 
   DG & \makecell{\textbf{0.15} $\pm$0.02\\Var:0.1\\ES:89\%} & \makecell{\textbf{0.39} $\pm$0.03\\Var:0.2\\ES:78\%} & \makecell{\textbf{0.33} $\pm$0.02\\Var:0.2\\ES:66\%} \\ 
   \hline
    \label{rep_erase}
\end{tabular}
\end{table}

### 2018-09-02 paper/content/inverted_u.tex
attempt to make the figures look better

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Wed Aug 15 19:03:20 2018
\begin{table}[ht]
\centering
\caption{Temporary Monopoly Heavy Tail X = 200}
\begin{tabular}{rlll}
  \hline
 & TS & DEG &  DG \\
  \hline
TS & \makecell{\textbf{0.003} $\pm$0.003\\Var:0.002\\ES:100\%} & \makecell{\textbf{0.083} $\pm$0.02\\Var:0.07\\ES:97\%} & \makecell{\textbf{0.17} $\pm$0.02\\Var:0.1\\ES:95\%} \\
  DEG & \makecell{\textbf{0.045} $\pm$0.01\\Var:0.03\\ES:92\%} & \makecell{\textbf{0.25} $\pm$0.02\\Var:0.1\\ES:75\%} & \makecell{\textbf{0.23} $\pm$0.02\\Var:0.1\\ES:78\%} \\
   DG & \makecell{\textbf{0.12} $\pm$0.02\\Var:0.08\\ES:88\%} & \makecell{\textbf{0.36} $\pm$0.03\\Var:0.2\\ES:76\%} & \makecell{\textbf{0.3} $\pm$0.02\\Var:0.1\\ES:64\%} \\
   \hline
\end{tabular}
\label{ht_incum}
\caption*{\tiny{The columns represent the strategy of the incumbent and the rows represent the strategy of the entrant. The first line in each cell contains the average market share for the entrant over $N=1000$ simulations as well as a 95\% confidence interval. The second line contains the sample variance of the observed market shares and the third line contains the fraction of simulations that ended up with one firm getting $> 90\%$ of the market. Note that smaller values in the table are better for the incumbent. Market shares are calculated as the fraction of users selecting a particular firm \textit{after} the entrant has already entered (i.e. the free rounds to firm 2 do not count towards the share)}}
\end{table}

>>>>

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Wed Aug 15 19:03:20 2018
\begin{table}[ht]
\centering
\caption{Temporary Monopoly Heavy Tail X = 200}
\begin{tabular}{rlll}
\hline
\multicolumn{4}{c}{Incumbent Algorithm}\\
\multirow{12}{0.6in}{\rotatebox{90}{Entrant Algorithm}} \\
  \hline
 & TS & DEG &  DG \\
  \hline
TS & \makecell{\textbf{0.003} $\pm$0.003\\Var:0.002\\ES:100\%} & \makecell{\textbf{0.083} $\pm$0.02\\Var:0.07\\ES:97\%} & \makecell{\textbf{0.17} $\pm$0.02\\Var:0.1\\ES:95\%} \\
  DEG & \makecell{\textbf{0.045} $\pm$0.01\\Var:0.03\\ES:92\%} & \makecell{\textbf{0.25} $\pm$0.02\\Var:0.1\\ES:75\%} & \makecell{\textbf{0.23} $\pm$0.02\\Var:0.1\\ES:78\%} \\
   DG & \makecell{\textbf{0.12} $\pm$0.02\\Var:0.08\\ES:88\%} & \makecell{\textbf{0.36} $\pm$0.03\\Var:0.2\\ES:76\%} & \makecell{\textbf{0.3} $\pm$0.02\\Var:0.1\\ES:64\%} \\
   \hline
\end{tabular}
\label{ht_incum}
\caption*{\tiny{The first line in each cell contains the average market share for the entrant over $N=1000$ simulations as well as a 95\% confidence interval. The second line contains the sample variance of the observed market shares and the third line contains the fraction of simulations that ended up with one firm getting an ``extreme" market share of $> 90\%$. Note that smaller values in the table are better for the incumbent. Market shares are calculated as the fraction of users selecting a particular firm \textit{after} the entrant has already entered (i.e. the free rounds to the incumbent do not count towards the share)}}
\end{table}

### 2018-09-02 paper/content/revisited.tex
attempt to make the figures look better

\begin{figure}[ht]
\caption{Relative Reputation Plots}
\includegraphics[scale=0.35]{figures/relative_uniform_annotated_plot}
\includegraphics[scale=0.35]{figures/ts_dg_nih_10_prelim}
\caption*{\tiny{The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of both of the algorithms on a given instance and then calculate the proportion of runs where $\TS \geq \DG$. The shaded area display 95\% confidence intervals.}}
\label{relative_rep_plots}

>>>>

\begin{figure}[ht]
\caption{Relative Reputation Proportion Plots for $\TS$ vs $\DG$. Shaded area display 95\% confidence intervals.}
\includegraphics[scale=0.35]{figures/relative_uniform_annotated_plot}
\includegraphics[scale=0.35]{figures/relative_nih_ts_dg.png}
%\caption*{\tiny{The plots contain the average reputation over $1000$ runs for a memory size of $100$ where, for a given $t$, we record the reputation of both of the algorithms on a given instance and then calculate the proportion of runs where $\TS \geq \DG$. The shaded area display 95\% confidence intervals.}}
\label{relative_rep_plots}
